Gut-resident microorganisms and their genes are associated with cognition and neuroanatomy in children

### 2023-10-06 manuscript/main.tex
fixed previous reference to S salivarius
cog-brain-taxa discussion paragraph

Among these, \emph{A. hadrus} is the variable with 
highest average relative importance along all reported 
(mean = 1.7\%; min = 1.0\%; max = 3.8\%, Figure 4B-C).
\emph{B. wexlerae}, which was important in RF models of cognitive function,
and was the only species to be significantly associated
with cogntive function in young children using LMs, 
was also important in models of the entorhinal, fusiform and lingual areas
and had the highest importance in models predicting the size of
both the left and right right parahippocampus.
Another cluster of model importance contained taxa associated with the
basal forebrain, especially the cingulate and the accumbens. This
cluster contains \emph{B. ovatus} and \emph{B. uniformis},
but also \emph{Alistipes finegoldii and Streptococcus salivaris}.

@@

>>>>

Among these, \emph{A. hadrus} is the variable with 
highest average relative importance along all reported 
(mean = 1.7\%; min = 1.0\%; max = 3.8\%, Figure 4B-C).
\emph{B. wexlerae}, which was important in RF models of cognitive function,
and was the only species to be significantly associated
with cogntive function in young children using LMs, 
was also important in models of the entorhinal, fusiform and lingual areas
and had the highest importance in models predicting the size of
both the left and right right parahippocampus.
Another cluster of model importance contained taxa associated with the
basal forebrain, especially the cingulate and the accumbens. This
cluster contains \emph{B. ovatus} and \emph{B. uniformis},
but also \emph{Alistipes finegoldii and S. salivarius}.

@@

Our ability to probe individual cognitive subscales provided
results that also endorse previous findings and lay insight to
potential gut-microbial connections between cognition and neuroanatomy.
For example, a longitudinal neurocognitive development study pointed at bilateral
associations between the thalamus and the EL component of the Mullen scales.
Linking to this observation, we found previously-mentioned taxa such as 
\textit{B. wexlerae} and \textit{A. hadrus} to be among the top 15\% important predictors
on both left and right thalamus and the EL subscale.
Another instance of those findings is a previously reported association between
the central opercular cortex (COC) and Gross Motor development. In this case, we identified that
butyrate-producing \textit{Fusicatenibacter saccharivorans} is among the 15\% most important predictors
for both the GM subscale and three bilateral components of the COC
(left and right pars orbitalis, pars opercularis and pars triangularis).
Previous results also link to relationships between the caudate and the cerebellum,
and the Visual Reception score.
\textit{S. salivarius} was consistently found among the top 20\% predictors for this subscale, along with
both sides of the thalamus and cerebellum white matter, along with cerebellar vermal lobules I-X.
